% Resume master document.
% Copyright (C) 2015-2019 Kieran Colford
%
% All rights reserved.

\documentclass[11pt,letterpaper,final]{moderncv}

% moderncv theme
\moderncvtheme{casual}

% misc
\usepackage[utf8]{inputenc}
%\usepackage{hyperref}
\usepackage[scale=0.80]{geometry}
\recomputelengths

% personal info
\name{Kieran}{Colford}
\address{97 Arundel Ave.}{Toronto, ON, M4K 3A3}{Canada}
\email{kieran@kcolford.com}
\homepage{www.kcolford.com}
\social[linkedin]{kierancolford}
\social[github]{kcolford}
\extrainfo{StackOverflow: randomusername (over 6,000 reputation)}

\begin{document}

\makecvtitle

%% Candidate for Bachelor of Computer Science at the University of
%% Waterloo, term 3B.

\section{Summary of Qualifications}

\cvlistitem{Extensive professional work experience gained across many
  business structures (startup, government/military, finance) and
  technologies (frontend, backend, infrastructure, machine learning,
  mobile).}

\cvlistitem{Successfully delivered projects individually and as a team
  in private and open source settings.}

\cvlistitem{Consistently recognized as a hard working, self-motivated
  team leader.}

\cvlistitem{Canadian Citizen}

\cvcomputer{Languages}{Rust, C/C++, C\#, Go, Java, Python,
  Javascript/NodeJS, SQL, and Swift}{Devops}{GIT, Github, Gitlab,
  Jenkins, CircleCI, TravisCI, Docker, Vagrant, and Ansible}

\cvcomputer{Cloud}{AWS, Digital Ocean, Google Cloud, Firebase, Heroku,
  Open Stack, Cloudflare, and Netlify}{Technologies}{Linux (Arch
  Linux), GatsbyJS, PWA, Tensorflow, WebAssembly, and PostgeSQL}

\cvcomputer{Frameworks}{Cordova, React, {}.NET, Native iOS, Rails,
  Django, and Native Android}{Business}{Scrum, Agile, Slack, Trello,
  and Requirements Gathering}

\section{Education}

\cventry{2014--present}{Candidate for Bachelor of Computer
  Science}{University of Waterloo}{Waterloo, Ontario}{Term 3B}{}

\section{Experience}

\cventry{Jan.--Apr. 2019}{Senior Development Lead}{R.C.A.F Aerospace
  Warfare Centre, Innovation Lab}{Kitchener,
  Ontario}{}{\begin{itemize}
  \item Provided guidance and mentorship to junior developers based on
    experience gained in multiple technical roles.
  \item Designed, developed and deployed first mobile financial
    processing application from problem definition through fleet-wide
    adoption.
  \item Led the adoption of best practice software development
    life-cycle tooling including CI/CD, containerization and cloud
    services.
  \end{itemize}}

\cventry{Sept. 2017--Apr. 2018}{Fullstack Software
  Developer}{University of Waterloo, Computer Science Computing
  Facility}{Waterloo, Ontario}{}{\begin{itemize}
  \item Used machine learning to design and build an Optical Character
    Recognition pipeline.
  \item Maintained and improved software and services essential to
    university operations.
  \item Converted a large legacy code base from Python 2 to Python 3.
  \end{itemize}}

\cventry{May.--Aug. 2016 and Jan.--Apr. 2017}{Fullstack Software
  Developer}{BlueRover}{Kitchener, Ontario}{}{\begin{itemize}
  \item Engineered a trend analytics engine that identifies potential
    hazards in food preparation thanks to data provided by the
    I.O.T. (Internet of Things) infrastructure.
  \item Maintained and expanded major product offerings using
    innovative tools and techniques.
  \item Independently developed a multitude solutions for our existing
    product base in an agile environment.
  \end{itemize}}

\iffalse

\cventry{Sept.--Dec. 2015}{Software Developer}{Ontario Teacher's
  Pension Plan}{Toronto, Ontario}{}{\begin{itemize}
  \item Received an outstanding work term evaluation from my employer.
  \item Reverse engineered the database for a third party product, and
    then developed an app for non-developers to view relevant content
    of the database.
  \item Designed and produced a backwards compatible service for
    sending email from enterprise applications.
  \end{itemize}}

\cventry{Jul.--Aug. 2013 and Jul.--Aug. 2014}{Sailing Instructor}{Camp
  Tamarack Ltd.}{Bracebridge, Ontario}{}{\begin{itemize}
  \item Appointed interim Head of Sailing whenever the usual head (my
    supervisor) was unavailable (day off, arranging special events,
    etc.)
  \item Supervised young children in open water environment, acting as
    both a teacher and a life guard.
  \item Exhibited excellent teamwork skills through the fostering of
    strong work relationships.
  \end{itemize}}

\section{Education}

\cventry{2014--present}{Candidate for Bachelor of
  Mathematics}{University of Waterloo}{Waterloo, Ontario}{}{}

\cventry{2014}{Ontario Secondary School Diploma}{The Abelard
  School}{}{}{}

\section{Awards}

\cventry{2014}{Evgeny Kravchenko Memorial Scholarship}{University of
  Waterloo}{}{}{}

\cventry{2014}{University of Waterloo President’s
  Scholarship}{University of Waterloo}{}{}{}

\cventry{2014}{AP Scholar with Distinction}{The College
  Board}{}{}{Awarded for receiving an average score of at least 3.5 on
  all AP Exams taken, and scores of 3 or higher on five or more of
  these exams.}

\cventry{2014}{The Alan Turing Award for Excellence in Computer
  Science}{The Abelard School}{}{}{}

\cventry{2014}{Ontario Scholar Certificate}{The Abelard School}{}{}{}

\section{Projects}

\cventry{2017}{Dynamic DNS}{}{}{}{Designed and developed software to
  dynamically update DNS records for nodes without static IP addresses
  for reducing costs and improving usability of mobile workstations.}

\cventry{2016}{Linux Firmware Support}{}{}{}{Developed firmware for
  supporting the Atmel MaxTouch Touchscreen in the Lenovo Thinkpad
  Yoga 11e Chromebook (and other devices such as the Google Pixel 2)
  on vanilla Linux kernels.}

\cventry{2016}{Personal Enterprise Infrastructure}{}{}{}{Networked
  together all personal computing platforms, from Chromebook to cloud
  virtual machines and containers to desktop, in an enterprise grade
  infrastructure based on Arch Linux.}

\cventry{2016}{Port of GCC to Course Specific
  Architecture}{}{}{}{Ported the GCC to a varient of MIPS specific to
  the CS 241 course in which students write their own compiler.
  \emph{(could not publish)}}

\cventry{2015}{UWaterloo AddCourse}{}{}{}{A Python App that eases the
  task of getting into courses after the course selection date.}

\cventry{2014}{Boilerplate Generator}{}{}{}{Developed an easy to use
  boilerplate generator that analyzes comments in source code and
  generates code based on those comments.}

\cventry{2014}{Mongoose}{}{}{}{A fully fledged compiler for a Turing
  Complete subset of the C language.}

\fi

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
